Titulo

### 2015-09-18 Paper/ms.tex
updates

@@

We propose a simplified model in which the galaxy is modeled as an sphere undergoing solid-body rotation, with an homogeneous mixture of dust and hydrogen at a constant temperature. The solid-body rotation does not induce any spatial anisotropy in the integrated line flux, the escape fraction or in the average number of scatterings. This symmetry allows to the creation of an analytic approximation for the galaxy spectrum  proposed, see \cite{Garavito14} for details. In this model the optical depth $\tau_{H}$, the  rotation velocity $V_{max}$ and the inclination angle $\theta$ are free parameters. \\

The outcoming spectra of the rotating galaxy is then affected by a symmetric thin shell of expanding gas at a constant velocity following the model proposed by \cite{2014arXiv1404.2958V, Orsi12}.   \\

@@

\section{Theoretical Background}
\label{sec:theo}
In this section we describe the two different models that together are used to reproduce a real and consistent \lya profile. The first one is a rotation model for the galaxy and the second is a thin shell model for the outflow. \\

We use the simplified rotation model developed by \citep{Garavito14} in which a rotating galaxy is modeled as a solid rotating sphere, with a homogeneous mixture of hydrogen and dust. Photons are initially at the center of the sphere. The equations governing this solid-body rotation sphere in which the axis of rotation is defined to be align with the $z$-axis are: \\

CAMBIAR ESTOOOOO

Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear velocity at the sphere's surface. The minus/plus sign in the $x$/$y$-component of the velocity indicates the direction of rotation. In this case we take the angular velocity in the same direction as the $\hat{k}$ unit vector. \\

@@

These galaxies have gas fractions close to $20\%$ \citep{Narayanan2012}. We approximate that the hydrogen content is
$20\%$ the total baryonic content from the cosmological baryon to dark matter  abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015}, multiplied by a primordial Hydrogen fraction of $0.75$. All these considerations gives us hydrogen masses in the range $2.7\times 10^{8}-2.7\times 10^{9}$\Msun.\\

From these constraints we chose to model two kinds of central galaxies in the extremes of these distributions. The first has $\tau =2\times 10^5$ and a rotational velocity of $60$\kms. The second has $\tau=2\times 10^6$ and a rotational velocity of $125$\kms.\\

We have then 3 parameters left that are going to vary along a wide range. These are: the galaxy rotation velocity \vgal, the outflow hydrogen column density \nh and the outflow expanding velocity \vout.\\

\vgal covers 3 different angles: $20$ \kms, $100$ \kms and $200$ \kms. \lognh takes 41 different values from $20.0$ to $22.5$. And \vout covers 5 equidistant velocities from $100$ \kms to $500$ \kms. The permutations of these three are analyzed in section \ref{sec:results}. \\

In order to study the influence of each of the three free parameters, we fix two of them and see how the final spectrum varies along the other one left. In each case we will state these changes. \\

\subsection{Influence of the Galaxy Rotation Velocity: \vgal}

\subsection{Influence of the Galaxy Outflow Velocity: \vout }

\subsection{Influence of the Galaxy Optical Depth: $\tau$ }

@@

---------------------------------------------------------------------\\
MISSING: \\
- Comparison with some other result (probably observations).\\
- Why is this result useful? \\
- What possible implications can this model have?\\
-----------------------------------------------------------------------\\

@@

We use an outflow model that follows the characteristics put described in \citep{Verhamme06} with the code presented in\citep{Orsi12}.  The outflow consists of an isothermal, spherical flow expanding at
constant velocity \vel.  The outflow is empty inside the shell's inner radius $R_{in}$ and reaches out to an external radius $R_{out}$. The relationship between these two radii is parameterized by $R_{in} =
f_{th}R_{out}$, with $f_{th}=0.9$ as the fiducial value. The temperature of the medium is assumed constant and equal to $T=10^4 K$ which sets the velocity dispersion of Maxwell-Boltzmann distributions to $v_{\rm th}=12.84$\kms. \\

@@

We have then 3 parameters left that are going to vary along a wide range. These are: the galaxy rotation velocity \vgal, the outflow hydrogen column density \nh and the outflow expanding velocity \vout. \\

\vgal covers 3 different angles: $20$ \kms, $100$ \kms and $200$ \kms. \lognh takes 41 different values from $20.0$ to $22.5$. And \vout covers 5 equidistant velocities from $100$ \kms to $500$ \kms. The permutations of these three are analyzed in section \ref{sec:results}. \\

@@

\subsection{Influence of the Galaxy Rotation Velocity: \vgal}

If one sets fixed outflow \vout and \lognh in each case the rotation velocity has the same effect: it increases proportionally the intensities. However this change is not that significant. The resulting spectra are completely the same, but enlarged vertically by a small factor. Fig. \ref{fig:influence_vgal} helps visualize this effect in a better way.\\

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=0.5\textwidth]{./figures/inf_vgal_soft.png}
\end{center}
\caption{\textbf{Influence of Galaxy Rotation Velocity:} The values of the fixed parameters are \vout = $100$ \kms and \lognh = $20.9375$. The 3 possible velocities are shown in the plot with different line styles. The increase is visible as well as its small enlargement factor.\\
\label{fig:influence_vgal}}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=0.5\textwidth]{./figures/inf_lognh_soft.png}
\end{center}
\caption{\textbf{Influence of Outflow Hydrogen Column Density:} The values of the fixed parameters are \vout = $100$ \kms and \vgal = $100$ \kms. There are three stages of the \lognh value shown: initial, intermediate and final, with the values shown on the plot.\\
\label{fig:influence_lognH}}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=0.5\textwidth]{./figures/inf_vout1_soft.png}
\end{center}
\caption{\textbf{Influence of Outflow Expanding Velocity:} The values of the fixed parameters are \lognh = 20.125 and \vgal = $100$ \kms.\\
\label{fig:influence_vout1}}
\end{figure}

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=0.5\textwidth]{./figures/inf_vout2_soft.png}
\end{center}
\caption{\textbf{Influence of Outflow Expanding Velocity:} The values of the fixed parameters are \lognh = 21.25 and \vgal = $100$ \kms.\\
\label{fig:influence_vout2}}
\end{figure}

>>>>

We propose a simplified model in which the galaxy is modeled as an sphere undergoing solid-body rotation, with an homogeneous mixture of dust and hydrogen at a constant temperature, that is also expanding in the radial direction due to outflows. In this model the optical depth \tauh, the  rotation velocity \vrot and the outflow velocity \vout are free parameters. \\

@@

@@

\section{Theoretical Background}
\label{sec:theo}
In this section we describe the proposed model used to reproduce a real and consistent \lya profile. \\

\subsection{Model}

We use the simplified rotation model developed by \citep{Garavito14} in which a rotating galaxy is modeled as a solid rotating sphere, with a homogeneous mixture of hydrogen and dust. There is also the radial expanding velocity. Photons are initially at the center of the sphere. These two velocities are added by components as follows. The equations governing this movement in which the axis of rotation is defined to be align with the $z$-axis are: \\

\begin{equation}
v_{x}=\frac{x}{R}v_{\rm out}-\frac{y}{R}v_{\rm rot}, \label{subeq1}
\end{equation}

\begin{equation}
v_{y}=\frac{y}{R}v_{\rm out}+\frac{x}{R}v_{\rm rot}, \label{subeq2}
\end{equation}

\begin{equation}
v_{z}=\frac{z}{R}v_{\rm out}, \label{subeq3}
\end{equation}

Where $R$ is the radius of the sphere. The minus/plus sign in the $x$/$y$-component of the rotation velocity part indicates the direction of rotation. In this case we take the angular velocity in the same direction as the $\hat{k}$ unit vector. \\

@@

\subsection{Galaxy Parameters}

Our aim is to provide a realistic baseline to compare against observations of LAEs at $z\sim 3$. It has been found by analysis of the abundance and angular correlation function that LAEs reside in DM halos of masses in the range $10^{10}-10^{11}$\Msun \cite{WalkerSoler2012}. This mass range corresponds to maximum circular velocities in the range $60-125$\kms and a median halo scale radius of $15$kpc. \footnote{These results were found using the  N-body data available in \url{www.cosmosim.org}}. \\

CAMBIAR ESTOOOOO (cambie 10E9 por 10E10)\\

These galaxies have gas fractions close to $20\%$ \citep{Narayanan2012}. We approximate that the hydrogen content is $20\%$ the total baryonic content from the cosmological baryon to dark matter  abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015}, multiplied by a primordial Hydrogen fraction of $0.75$. All these considerations gives us hydrogen masses in the range $2.7\times 10^{8}-2.7\times 10^{10}$\Msun.\\

These choices give us a range for the number density of Hydrogen atoms of $4\times10^{-4}-4\times 10^{-3}$ atoms cm$^{-3}$. With a Lyman-$\alpha$ cross section at the line center of $\sigma_{H}=1.0\times 10^{-14}$ cm$^{2}$ we finally obtain that the optical depth from the cloud's center  should be in the range $\tau_{\rm H}=2 \times 10^{5} - 2 \times 10^{7}$.  \\

In order to be able to tell the influence of the rotation and outflow velocities in the \lya line morphology, a mapping of them is made without concerning of their physical meaning at first. The following ranges are selected for these parameters: \vrot in $0,100,200,300$ \kms and \vout in $100,200,300$ \kms.\\

%From these constraints we chose to model two kinds of central galaxies in the extremes of these distributions. The first has $\tau =2\times 10^5$ and a rotational velocity of $60$\kms. The second has $\tau=2\times 10^6$ and a rotational velocity of $125$\kms.\\

%For the first stage there are two fixed parameters: the optical depth $\tau = 10^8$ and the galaxy viewing angle \ang = $90^\circ$. For the second stage there is one fixed parameter: the metallicity of the outflow $Z=-4.0$. This 3 fixed values are selected because the characteristics of observed LAEs, especially their low mass and their highest star formation rate of all. \\

%We have then 3 parameters left that are going to vary along a wide range. These are: the galaxy rotation velocity \vrot, the outflow hydrogen column density \nh and the outflow expanding velocity \vout.\\

%\vrot covers 3 different angles: $20$ \kms, $100$ \kms and $200$ \kms. \lognh takes 41 different values from $20.0$ to $22.5$. And \vout covers 5 equidistant velocities from $100$ \kms to $500$ \kms. The permutations of these three are analyzed in section \ref{sec:results}. \\

%The results of this project consist of emulating a LAE spectrum basing on its physical characteristics defined by the 3 free parameters we stated before. When defined the combination of those three. \\

%In the following subsection each free parameter is explained deeper. \\

%In order to study the influence of each of the three free parameters, we fix two of them and see how the final spectrum varies along the other one left. In each case we will state these changes. \\

\section{Results}

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=0.5\textwidth]{./figures/tau10E5.png}
\end{center}
\caption{\textbf{\lya profile for \tauh$=10^5$:} With \vrot ranging $0,100,200,300$ \kms and \vout ranging $100,200,300$ \kms.
\label{fig:tau10E5}}
\end{figure}

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=0.5\textwidth]{./figures/tau10E6.png}
\end{center}
\caption{\textbf{\lya profile for \tauh$=10^6$:} With \vrot ranging $0,100,200,300$ \kms and \vout ranging $100,200,300$ \kms.
\label{fig:tau10E6}}
\end{figure}

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=0.5\textwidth]{./figures/tau10E7.png}
\end{center}
\caption{\textbf{\lya profile for \tauh$=10^7$:} With \vrot ranging $0,100,200,300$ \kms and \vout ranging $100,200,300$ \kms.
\label{fig:tau10E7}}
\end{figure}

\subsection{Influence of the Galaxy Rotation Velocity: \vrot}

\subsection{Influence of the Galaxy Outflow Velocity: \vout}

\subsection{Influence of the Galaxy Optical Depth: \tauh}

@@

---------------------------------------------------------------------\\
TO ADD: \\
- Comparison with some other result (probably observations).\\
- Why is this result useful? \\
- What possible implications can this model have?\\
-----------------------------------------------------------------------\\

@@

We use an outflow model that follows the characteristics put described in \citep{Verhamme06} with the code presented in\citep{Orsi12}.  The outflow consists of an isothermal, spherical flow expanding at
constant velocity \vout.  The outflow is empty inside the shell's inner radius $R_{in}$ and reaches out to an external radius $R_{out}$. The relationship between these two radii is parameterized by $R_{in} =
f_{th}R_{out}$, with $f_{th}=0.9$ as the fiducial value. The temperature of the medium is assumed constant and equal to $T=10^4 K$ which sets the velocity dispersion of Maxwell-Boltzmann distributions to $v_{\rm th}=12.84$\kms. \\

@@

We have then 3 parameters left that are going to vary along a wide range. These are: the galaxy rotation velocity \vrot, the outflow hydrogen column density \nh and the outflow expanding velocity \vout. \\

\vrot covers 3 different angles: $20$ \kms, $100$ \kms and $200$ \kms. \lognh takes 41 different values from $20.0$ to $22.5$. And \vout covers 5 equidistant velocities from $100$ \kms to $500$ \kms. The permutations of these three are analyzed in section \ref{sec:results}. \\

@@

\subsection{Influence of the Galaxy Rotation Velocity: \vrot}

If one sets fixed outflow \vout and \lognh in each case the rotation velocity has the same effect: it increases proportionally the intensities. However this change is not that significant. The resulting spectra are completely the same, but enlarged vertically by a small factor. Fig. \ref{fig:influence_vrot} helps visualize this effect in a better way.\\

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.5\textwidth]{./figures/inf_vgal_soft.png}
\end{center}
\caption{\textbf{Influence of Galaxy Rotation Velocity:} The values of the fixed parameters are \vout = $100$ \kms and \lognh = $20.9375$. The 3 possible velocities are shown in the plot with different line styles. The increase is visible as well as its small enlargement factor.\\
\label{fig:influence_vrot}}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=0.5\textwidth]{./figures/inf_lognh_soft.png}
\end{center}
\caption{\textbf{Influence of Outflow Hydrogen Column Density:} The values of the fixed parameters are \vout = $100$ \kms and \vrot = $100$ \kms. There are three stages of the \lognh value shown: initial, intermediate and final, with the values shown on the plot.\\
\label{fig:influence_lognH}}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=0.5\textwidth]{./figures/inf_vout1_soft.png}
\end{center}
\caption{\textbf{Influence of Outflow Expanding Velocity:} The values of the fixed parameters are \lognh = 20.125 and \vrot = $100$ \kms.\\
\label{fig:influence_vout1}}
\end{figure}

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=0.5\textwidth]{./figures/inf_vout2_soft.png}
\end{center}
\caption{\textbf{Influence of Outflow Expanding Velocity:} The values of the fixed parameters are \lognh = 21.25 and \vrot = $100$ \kms.\\
\label{fig:influence_vout2}}
\end{figure}
